Using the internal language of toposes in algebraic geometry

### 2015-11-22 slides-ihes2015.tex
typo

  \begin{center}
    \small
    \begin{tabular}{ll}
      \toprule
      externally to $\Sh(X)$ & internally \\
      \midrule
      sheaf of rings & ring \\
      sheaf of modules & module \\
      sheaf of finite type & finitely generated module \\
      finite locally free sheaf & finite free sheaf \\
      \bottomrule
    \end{tabular}
  \end{center}

@@

  \only<2->{
    Let~$X$ be a scheme. Depending on~$\Diamond$,~$\Sh(X)
    \models \Diamond\varphi$ means that~$\varphi$ holds on \ldots
    \begin{itemize}
      \item \ldots{} a dense open subset.
      \item \ldots{} a given open subset~$U$.
      \item \ldots{} an open subset containing a given closed subset~$A$.
      \item \ldots{} a neighbourhood of a given point~$x \in X$.
    \end{itemize}

>>>>

  \begin{center}
    \small
    \begin{tabular}{ll}
      \toprule
      externally to $\Sh(X)$ & internally \\
      \midrule
      sheaf of rings & ring \\
      sheaf of modules & module \\
      sheaf of finite type & finitely generated module \\
      finite locally free sheaf & finite free module \\
      \bottomrule
    \end{tabular}
  \end{center}

@@

  \only<2->{
    Let~$X$ be a scheme. Depending on~$\Diamond$,~$\Sh(X)
    \models \Diamond\varphi$ means that~$\varphi$ holds on \ldots
    \begin{itemize}
      \item \ldots{} a dense open subset.
      \item \ldots{} a given open subset~$U$.
      \item \ldots{} an open subset containing a given closed subset~$A$.
      \item \ldots{} an open neighbourhood of a given point~$x \in X$.
    \end{itemize}
